---
title: "CARPS Reproducibility Report"
output:
  html_document:
    toc: true
    toc_float: true
---

#### Article ID: 9-5-2015
#### Pilot 1: Kari Leibowitz
#### Co-pilot: Yochai Shavit
#### Start date: 11/1/17
#### End date: [Insert end date - use US format]   

-------

#### Methods summary: 
Here, the authors showed participants in four age groups pairs of faces that were pre-determined to be high or low in three traits: niceness (trustworthiness), intelligence, or strength (dominance). The authors then assessed the ability of these age groups to accurately identify which of two faces was high in a particular trait, and the consistency of these different age groups to each other in terms of the ability to "correctly" identify traits of faces based on a pre-determined consensus. 

------

#### Target outcomes: 

For this article we focused on the findings reported in the results section of Experiment 1.

Specifically, we should attempted to reproduce all descriptive and inferential analyses reported in the text below and associated tables/figures:

> Figures 2, 3, and 4 summarize results for all age groups
and traits; higher percentages of expected responses (i.e.,
those predicted on the basis of prior data—e.g., that
trustworthy faces would be identified as nice and untrustworthy
faces as mean) indicate stronger consensus. Combined, all four age groups showed significant consensus
compared with chance (50%) when identifying
faces as mean or nice (93%; Fig. 2), strong or not strong
(85%; Fig. 3), and smart or not smart (76%; Fig. 4).
Critically, all age groups attributed all three traits with
significant consensus, ps < .001, ds > 1.08. However, an
analysis of variance (ANOVA) revealed a significant main
effect of age group, F(3, 236) = 17.91, p < .001. Although
3- to 4-year-olds responded with robust and adult like
consensus (72% across all traits), they were less consistent
than 5- to 6-year-olds (81%), 7- to 10-year-olds (88%),
and adults (89%). One-way ANOVAs followed by post hoc tests with Sidak corrections for multiple comparisons
were used to analyze age differences for each trait. These
analyses revealed that when attributing both trustworthiness
and dominance, 3- to 4-year-olds were less consistent
than all other age groups (all ps < .01, ds > 0.59),
which exhibited equivalent consistency (all ps > .23, ds <
0.40).


------

[The chunk below sets up some formatting options for the R Markdown document]

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

## Step 1: Load packages

[Some useful packages are being loaded below. You can add any additional ones you might need too.]

```{r}
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(CARPSreports) # custom report functions
library(effsize)
```

## Step 2: Load data

```{r}
setwd("~/Desktop/251")
d<- read.csv("CARPS_9-5-2014_PS/data/Cogsdill_FaceTrait_Experiment1Public_04Feb14.csv")

head(d)
```

## Step 3: Tidy data

Want to gather data into age groups for each variable 
```{r}

dtidy <- select(d, 'Age.Group', 'NICE', 'SMART', 'STRONG') 

summariseCC <- summarise(group_by(CCdataframeordered, Question, add=TRUE), mean = mean(response, na.rm=T), sd=sd(response, na.rm=TRUE), n=n(), se=sd/sqrt(n))

dtidy2 <- dtidy %>%
  gather(Attribute, Rating, -Age.Group)

summarised <- summarise(group_by(dtidy2, Age.Group, Attribute, add=TRUE), mean=mean(Rating, na.rm=T), sd=sd(Rating, na.rm=T), n=n(), se=sd/sqrt(n))

```

## Step 4: Run analysis

### Descriptive statistics

#### Figure 2 and associated data: NICE

Here recreating Figure 2, a bar graph of percentage of expected responses for niceness
```{r figure 2}

dnice <- summarised %>%
  filter(Attribute=="NICE")

ggplot(data=dnice, aes(x=Age.Group, y=mean, fill=Age.Group)) +
    geom_bar(stat="summary", fun.y="mean", position="dodge") +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=1)

```

Replicating this finding:
">Combined, all four age groups showed significant consensus
compared with chance (50%) when identifying
faces as mean or nice (93%; Fig. 2)... Cogsdill et al., page 1134"
```{r niceness average}

mean(dtidy$NICE, na.rm=T)

```
Mean = 92.9, consistent with paper's finding


#### Figure 3 and associated data: STRONG

Here recreating Figure 3, a bar graph of percentage of expected responses for strength/submissiveness
```{r figure 3}

dstrong <- summarised %>%
  filter(Attribute=="STRONG")

ggplot(data=dstrong, aes(x=Age.Group, y=mean, fill=Age.Group)) +
    geom_bar(stat="summary", fun.y="mean", position="dodge") +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=1)


```


Replicating this finding:
">Combined, all four age groups showed significant consensus compared with chance (50%) when identifying faces as...strong or not strong (85%; Fig. 3)... Cogsdill et al., page 1134""
```{r niceness average}

mean(dtidy$STRONG, na.rm=T)

```
Mean = 84.6, consistent with paper's finding


#### Figure 4 and associated data: SMART

```{r figure 4}

dsmart <- summarised %>%
  filter(Attribute=="SMART")

ggplot(data=dsmart, aes(x=Age.Group, y=mean, fill=Age.Group)) +
    geom_bar(stat="summary", fun.y="mean", position="dodge") +
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=1)

```

Replicating this finding:

">Combined, all four age groups showed significant consensus compared with chance (50%) when identifying faces as...smart or not smart (76%; Fig. 4). Cogsdill et al., page 1134"
```{r smartness average}

mean(dtidy$SMART, na.rm=T)

```
Mean = 75.9, consistent with paper's finding


#### Checking consistency across age groups

">Although 3- to 4-year-olds responded with robust and adult like consensus (72% across all traits), they were less consistent than 5- to 6-year-olds (81%), 7- to 10-year-olds (88%), and adults (89%). Cogsdill et al., page 1134"

```{r consistency by age group across traits}

d3_4 <- dtidy2 %>%
  filter(Age.Group=="3-4 year olds")
mean(d3_4$Rating)

d5_6 <- dtidy2 %>%
  filter(Age.Group=="5-6 year olds")
mean(d5_6$Rating)

d7_10 <- dtidy2 %>%
  filter(Age.Group=="7-10 year olds")
mean(d7_10$Rating)

dadults <- dtidy2 %>%
  filter(Age.Group=="Adults")
mean(dadults$Rating)
```

Average across 3-4 year olds: 71.5%
Average across 5-6 year olds: 81.4%
Average across 7-10 year olds: 88.2%
Average across adults: 88.8%
All consistent with statistics reported in paper 

### Inferential statistics


#### Replicating consensus

Relicating this finding
">Combined, all four age groups showed significant consensus compared with chance (50%) when identifying faces as mean or nice , strong or not strong, and smart or not smart."

Looking at all four age groups combined for each of the three attributes. Here, we are using a chi squared test to compare the number of correct trials to the number of incorrect trials, although the authors do not specify exactly what statistical test was used to identify this concensus, so this is our best guess at what test was used. 

All ps<.001, consistent with author's finding.
```{r consensus compared with chance}

#multiplying each response by 9 since there were 9 trials, using that to compute # of correct and incorrect, inputting correct vs. incorrect into chi square test 
d$nice_correct <- round(9*d$NICE)
d$nice_wrong <- (9-d$nice_correct)
sum(d$nice_correct) #2007
sum(d$nice_wrong) #153
chisq.test(x=c(2007, 153))
#p<.001

d$smart_correct <- round(9*d$SMART)
d$smart_wrong <- (9-d$smart_correct)
sum(d$smart_correct) #1641
sum(d$smart_wrong) #519
chisq.test(x=c(1641, 519))
#p<.001

d$strong_correct <- round(9*d$STRONG)
d$strong_wrong <- (9-d$strong_correct)
sum(d$strong_correct) #1828
sum(d$strong_wrong) #332
chisq.test(x=c(1828, 332))
#p<.001

```


Replicating this finding:
">Critically, all age groups attributed all three traits with
significant consensus, ps < .001, ds > 1.08. from Cogsdill et al. page 1134"
Note: the authors don't specify what analytical test was used to determine consensus across age groups and there is some ambiguity in the phrasing here. We took this to mean that within each age group, ratings for each of the three attributes (nice, smart, strong) were consistent. In order to examine this, we looked at t tests and effect sizes for the percentage of correct and incorrect identifications using the "overall" variable across all attributes within each age group. However, it is unclear from the manuscript whether this was the correct approach. 

The paper also indicates that all ps <.001 and all ds>1.08. Using this method, we found that all ps were indeed < .001, but found that our smallest d was 1.42, indicating a potential discrepency between our findings and the paper's findings. However, without more information, it is unclear whether this discrepancy represents an error on our part or the part of the original authors, or simply that we did not replicate the same method described in the paper.


```{r overall}

#creating a variable for overall percentage of wrong identifications
d$overall_wrong <- (1-d$OVERALL)

#looking at t test for correct vs. incorrect trials over all 3 attributes for 3 to 4 year olds
d3_4overall <- d %>%
  filter(Age.Group=="3-4 year olds")
t.test(d3_4overall$OVERALL, d3_4overall$overall_wrong, paired=T)
cohen.d(d3_4overall$OVERALL, d3_4overall$overall_wrong, paired=T)
#p<.001, d=1.42

#looking at t test for correct vs. incorrect trials over all 3 attributes for 5 to 6 year olds
d5_6overall <- d %>%
  filter(Age.Group=="5-6 year olds")
t.test(d5_6overall$OVERALL, d5_6overall$overall_wrong, paired=T)
cohen.d(d5_6overall$OVERALL, d5_6overall$overall_wrong, paired=T)
#p<.001, d=2.37

#looking at t test for correct vs. incorrect trials over all 3 attributes for 7 to 10 year olds
d7_10overall <- d %>%
  filter(Age.Group=="7-10 year olds")
t.test(d7_10overall$OVERALL, d7_10overall$overall_wrong, paired=T)
cohen.d(d7_10overall$OVERALL, d7_10overall$overall_wrong, paired=T)
#p<.001, d=2.91

#looking at t test for correct vs. incorrect trials over all 3 attributes for adults
dadultoverall <- d %>%
  filter(Age.Group=="Adults")
t.test(dadultoverall$OVERALL, dadultoverall$overall_wrong, paired=T)
cohen.d(dadultoverall$OVERALL, dadultoverall$overall_wrong, paired=T)
#p<.001, d=3.19

```

Anova's go here 

Replicating this finding:
">However, an analysis of variance (ANOVA) revealed a significant main effect of age group, F(3, 236) = 17.91, p < .001. Cogsdill et al., page 1134"

Our results are consistent with this finding.

```{r}

summary(aov(OVERALL ~ Age.Group, data=d))
#F(3, 236) = 17.91, p<.001

```

Replicating this finding:
"> One-way ANOVAs followed by post hoc tests with Sidak corrections for multiple comparisons were used to analyze age differences for each trait. These analyses revealed that when attributing both trustworthiness and dominance, 3- to 4-year-olds were less consistent than all other age groups (all ps < .01, ds > 0.59), which exhibited equivalent consistency (all ps > .23, ds < 0.40). Cogsdill et al., page 1134"

```{r}

#first running one way anovas for each trait

summary(aov(NICE ~ Age.Group, data=d)) #p<.001, indicating difference between groups?
summary(aov(SMART ~ Age.Group, data=d)) #p<.001, indicating difference between groups?
summary(aov(STRONG ~ Age.Group, data=d)) #p<.001, indicating difference between groups?


with(d, pairwise.t.test(NICE, Age.Group, 
p.adj="sidak", paired=T))

```




## Step 5: Conclusion

[Include the carpsReport function below]

```{r}
# You can delete this commented text for your report, it is here to serve as a guide.
# Use the carpsReport() function in this code chunk.
# Here is a guide to the arguments you should include in the function:
# Report_Type: Enter 'pilot' or 'final'
# Article_ID: Enter the article's unique ID code
# Insufficient_Information_Errors: Enter the number of Insufficient Information Errors
# Decision_Errors Enter: the number of decision errors
# Major_Numerical_Errors: Enter the number of major numerical errors
# Time_to_Complete: Enter the estimated time to complete the report in minutes
# Author_Assistance: Enter whether author assistance was required (TRUE/FALSE)
# FOR EXAMPLE:
# carpsReport(Report_Type = "pilot", 
#             Article_ID = "ABhgyo", 
#             Insufficient_Information_Errors = 0, 
#             Decision_Errors = 1, 
#             Major_Numerical_Errors = 4, 
#             Time_to_Complete = 120, 
#             Author_Assistance = TRUE)
```

[Please also include a brief text summary describing your findings. If this reproducibility check was a failure, you should note any suggestions as to what you think the likely cause(s) might be.]

[This function will output information about the package versions used in this report:]

```{r session_info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info()
```
